Machine Learning Autoencoder Applied to Communication Channels

### 2019-06-18 Rapport/Article/Article.tex
Seance 06/18/2019

@@

@@

\subsection{Autoencoder}
Architecture, Training and simulation parameters, procedure to find a M epoch suitable, choices of p train, Talk about NN separation,

>>>>

Trainin set for array decoding.

@@

Trainin set for one-hot decoding, say how was pseudo-randomly generated, sa that the stastistic was checked to have 1/2 of 1s and 1/2 of 0s.

@@

However, we still need a decoding matrix.... Introduces autoencoder that could train without G

\subsection{Autoencoder}
Architecture, Training and simulation parameters, procedure to find a M epoch suitable, choices of p train, Talk about NN separation, no necessity for G, a slight different trainin approach (training data and labels are identical), same channel rate (16 units) for a message of 8 bits,
